---
output: github_document
---

[![Travis build status](https://travis-ci.com/muschellij2/recordscreen.svg?branch=master)](https://travis-ci.com/muschellij2/recordscreen)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/muschellij2/recordscreen?branch=master&svg=true)](https://ci.appveyor.com/project/muschellij2/recordscreen)
[![Coverage status](https://codecov.io/gh/muschellij2/recordscreen/branch/master/graph/badge.svg)](https://codecov.io/gh/muschellij2/recordscreen)
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# recordscreen Package: 

The goal of `recordscreen` is to provide functions to reccord the screen with `ffmpeg` to be able to show script execution.  A system installation `ffmpeg` is required, run to see if `ffmpeg` is in your `PATH`: 
```r
Sys.which("ffmpeg")
```

## Errors with Mac OSX Mojave and RStudio

You need to authorize RStudio to use the mic/camera in Mojave.  The changes were due to this: https://developer.apple.com/documentation/avfoundation/cameras_and_media_capture/requesting_authorization_for_media_capture_on_macos and fixed here https://github.com/rstudio/rstudio/issues/4579

If you an't access video/audio from RStudio IDE, then see issue here https://github.com/rstudio/rstudio/issues/4579. If you run into this,
make sure you have RStudio version >= 1.3.  To access this version download daily build https://dailies.rstudio.com/, authorize (use audio and opencv packages for force auth) 

```{r, eval = FALSE}
if (!requireNamespace("opencv"))
  install.packages("opencv")

library(opencv)
ocv_video(ocv_edges)
```

```{r, eval = FALSE}
if (!requireNamespace("audio"))
  install.packages("audio")

library(audio)
x <- rep(NA_real_, 50000)
# start recording into x
record(x, 22000, 1)
stopifnot(diff(range(x, na.rm = TRUE)) > 0)
```

Then download whatever RStudio you want.




  
- Make sure you go to System Preferences 
## Installation

You can install `recordscreen` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("muschellij2/recordscreen")
```
